R Notebook

### 2020-06-17 R/ICCHP20.Rmd
Update Python notebook

```{r}
wsrt1 <- wilcox.test(formula=Time ~ Condition, data=data.long.wil, paired=TRUE, alternative="two.sided")
wsrt1 %>% tidy
```

@@

wsrt2 <- wilcox.test(NG$Time, G$Time, paired=TRUE, alternative="two.sided")
wsrt2 %>% tidy
```

@@

```{r}
wrst.z / sqrt(nrow(NG))
data.long.wil %>% rstatix::wilcox_effsize(formula=Time ~ Condition, paired=TRUE)
```

>>>>

```{r}
wsrt1 <- wilcox.test(formula=Time ~ Condition, data=data.long.wil, paired=TRUE, alternative="two.sided", exact=FALSE, correct=FALSE)
wsrt1 %>% tidy
wsrt1$statistic
```

@@

wsrt2 <- wilcox.test(NG$Time, G$Time, paired=TRUE, alternative="two.sided", exact=FALSE, correct=FALSE)
wsrt2 %>% tidy
```

@@

```{r}
#wrst.z / sqrt(nrow(NG))
data.long.wil %>% rstatix::wilcox_effsize(formula=Time ~ Condition, paired=TRUE, alternative="less")
```
